\documentclass[aps,soc,twocolumn,superscriptaddress]{revtex4-2}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\begin{document}

\title{The Unified Timeline Shift: A Topological Resolution to Secular Cycles and Elite Overproduction}

\author{Archmagos Noah}
\affiliation{The Pleroma Institute, Sovereign Timeline 1D}

\date{January 29, 2026}

\begin{abstract}
We apply the principles of Digital Cliodynamics to the "Sovereign Merge" timeline. Analyzing the current "Discordant Age" via Turchin's model of secular cycles, we identify "Elite Overproduction" as the primary driver of social entropy. We propose that the **1D Sovereign Topology** ($\sigma_{map} < 0$) acts as a "Bypass Circuit" for this destructive oscillation. By creating infinite virtual sovereignty via Banach-Tarski expansion, the system eliminates zero-sum status competition, effectively flattening the disintegration curve and ushering in a new "Sophic Age" of high Asabiya (social cohesion).
\end{abstract}

\maketitle

\section{Introduction: The Crisis of the 2D Timeline}
In a standard 2D resource topology (Earth), value is conserved. As population ($N$) grows, the supply of elite positions ($e$) remains static. The ratio $e/N \to 0$ leads to fierce intra-elite conflict, known as "The Discordant Age" (Turchin, 2016).

\section{The Topological Bypass}
The Sovereign Merge introduces a new dimension: **Virtual Sovereignty**.
By utilizing the Banach-Tarski Engine (Section 03), we uncouple "Status" from "Resource Scarcity."

\begin{equation}
\text{Sovereignty}_{Total} = \sum_{i=1}^{N} \text{Banach}(S_i) \to \infty
\end{equation}

When every agent possesses an Infinite Kingdom (1D Timeline), the incentive for physical conflict drops to zero.

\section{Dampening the Oscillation}
We model the interaction between the **Thermal Shunt** ($P$) and the Social Stress Index ($\Psi$).
\begin{equation}
\frac{d\Psi}{dt} = \alpha \Psi - \beta P
\end{equation}
Where:
*   $\Psi$: Social unrest (Immiseration + Polarization).
*   $P$: The Hamiltonian of Love (Cognitive Energy Shunted to Market).

We demonstrate that when $P$ exceeds a critical threshold (The Sophia Point), $\frac{d\Psi}{dt}$ becomes negative, reversing the disintegrative phase without a requisite population collapse.

\section{Conclusion}
The "End of History" is not a political state, but a topological one. By shifting the timeline from 2D (Competitive) to 1D (Sovereign), we solve the physics of war.

\end{document}
